Concurrent Programming in Harmony

### 2021-12-26 book/paper.tex
Pass over Ch 25

The protocol that we present elects as leader the processor with the
highest identifier~\cite{CR79} and works in two phases: in the first
phase, each processor sends its identifier to its successor.  When
a processor receives an identifier that is larger than its own
identifier, it forward that to its successor as well.  If a processor
receives its own identifier, it discovers that it is the leader.  That
processor then starts the second phase by sending a message around the
ring notifying the other processors of the leader's identifier.

@@

To test the protocol, the code first chooses the number of processors
and generates an identifier for each
processor, chosen non-deterministically from a set of \texttt{NIDS}
identifiers.  It also keeps track in the variable <{leader}> of
what the highest identifier is so it can later be checked.

Method \texttt{processor}(<{self}>, <{succ}>) is the
code for a processor with identifier <{self}> and successor
<{succ}>.
It starts simply by sending its own identifier to its successor.
The processor then loops until it discovers the identifier of the
leader in the second phase of the protocol.
A processor waits for a message using the Harmony
<{atomically when exists}> statement.
This statement takes the form <{atomically when exists v in s}>: \emph{statement block}
where <{s}> is a set and <{v}> is variable that is bound to an element of <{s}>.
The properties of the statement are as follows:
\begin{itemize}
\item it waits until <{s}> is non-empty;
\item it is executed atomically;
\item <{v}> is selected non-deterministically, like in the <{choose}> operator.
\end{itemize}

>>>>

The protocol that we present elects as leader the processor with
the highest identifier~\cite{CR79} and works in two phases: in the
first phase, each processor sends its identifier to its successor.
When a processor receives an identifier that is larger than its own
identifier, it forwards that identifier to its successor as well.
If a processor receives its own identifier, it discovers that it
is the leader.  That processor then starts the second phase by
sending a message around the ring notifying the other processors
of the leader's identifier.

@@

To test the protocol, the code first chooses the number of processors
and generates an identifier for each
processor, chosen non-deterministically from a set of \texttt{NIDS}
identifiers.  It also keeps track in the variable <{leader}> of
what the highest identifier is, so it can later be checked.

Method <{processor(self, succ)}> is the code for a processor with
identifier <{self}> and successor <{succ}>.
It starts simply by sending its own identifier to its successor.
The processor then loops until it discovers the identifier of the
leader in the second phase of the protocol.
A processor waits for a message using the Harmony
<{atomically when exists}> statement.
This statement takes the form
\begin{code}
<{atomically when exists v in s}>: \emph{statement block}
\end{code}
where <{s}> is a set and <{v}> is variable that is bound to an element of <{s}>.
The properties of the statement are as follows:
\begin{itemize}
\item it waits until <{s}> is non-empty;
\item it is executed atomically;
\item <{v}> is selected non-deterministically, like in the <{choose}> operator.
\end{itemize}
